### 2020-08-21 spanish/sections/expertise.tex
Create expertise.tex
Update expertise.tex

\cvsection{Expertise}

@@

\cvskill
{Interests}
{Cabinets composition and allocation, ministerial turnover, political elites socialisation, civil service}

\cvskill
{}
{systems, political participation, digital media, electronic government}\\

>>>>

\cvsection{Especialidades}

@@

\cvskill
{Interests}
{Composición y nombramiento de gabinetes, rotación ministerial, socialización de élites políticas,}

\cvskill
{}
{sistemas de servicio civil, participación política, medios digitales, gobierno electrónico}\\
